WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-03 paper/reviews_ds.Rmd
suggestion for responding to C7

After making these definitions explicit, it becomes clear that the Reviewer's definition of replication as "a necessary steps towards reproducibility" is not consistent with the present paper.

@@

> These guidelines describe eight standards for open science,
the first seven of which "account for reproducibility of the reported results
based on the originating data, and for sharing sufficient information to conduct an independent 
replication" [@nosekPromotingOpenResearch2015a].
In this context, 
reproducibility can be defined as "re-performing the same analysis with the same code using a different analyst",
and replicability as "re-performing the experiment and collecting new data" [@patilVisualToolDefining2019].
These guidelines are: 1) Comprehensive
citation of literature, data, materials, and methods; 2) sharing data, 3)
sharing the code required to reproduce analyses, 4) sharing new research
materials, and 5) sharing details of the design and analysis; 6)
pre-registration of studies before data collection, and 7) pre-registration of
the analysis plan prior to analysis.
The eighth criterion is "not formally a transparency standard for authors", but "addresses 
journal guidelines for consideration of independent replications for publication".
WORCS defines the goals of open science in terms of the first seven TOP-guidelines,
and the workflow and its `R` implementation are designed to facilitate compliance therewith.

@@

Response: We apologize; it appears that there were numerous errors in the parsing of the reference list after rendering the manuscript to HTML - the preferred format of Data Science. The reference is indeed to the R-package. In the revised manuscript, we have repaired the references so that it is clear that this is a software package, et cetera.

@@

>>>>

After making these definitions explicit, it becomes clear that the Reviewer's definition of replication as "a necessary steps towards reproducibility" is not consistent with the definitions of the present paper.

@@

> These guidelines describe eight standards for open science,
the first seven of which "account for reproducibility of the reported results
based on the originating data, and for sharing sufficient information to conduct an independent 
replication" [@nosekPromotingOpenResearch2015a].
In this context, 
reproducibility can be defined as "re-performing the same analysis with the same code and the same data using a different analyst",
and replicability as "re-performing the experiment and collecting new data" [@patilVisualToolDefining2019].
These guidelines are: 1) Comprehensive
citation of literature, data, materials, and methods; 2) sharing data, 3)
sharing the code required to reproduce analyses, 4) sharing new research
materials, and 5) sharing details of the design and analysis; 6)
pre-registration of studies before data collection, and 7) pre-registration of
the analysis plan prior to analysis.
The eighth criterion is "not formally a transparency standard for authors", but "addresses 
journal guidelines for consideration of independent replications for publication".
WORCS defines the goals of open science in terms of the first seven TOP-guidelines,
and the workflow and its `R` implementation are designed to facilitate compliance therewith.

@@

Response: We apologize; it appears that there were numerous errors in the parsing of the reference list after rendering the manuscript to HTML - the preferred format of Data Science. The reference is indeed to the R-package. In the revised manuscript, we have repaired the references so that it is clear that this is a software package.

@@

We agree that GitHub is not an ideal platform for handling large data. However, it is ideal for handling version control of computer code, Markdown documents, and small to medium-sized data files. Larger files can be linked to git using git-annex (https://git-annex.branchable.com) and similar solutions. We now mention git-annex as a possible route to handle larger data files (TODO). We agree that it is important to make open data findable beyond just providing it freely. Digital object identifiers are the de-factor standard for making unique references to data sets. In line with the reviewer's suggestion, we suggest to use external providers to provide such DOIs while github is still the primary data storage. Our prefered route is to use github web hooks to link Zenodo and a WORCS-compatible repository. With this technique, Zenodo issues DOI for content hosted on github repositories including some nice extras, such as automatic badge DOI badges for the repository.
